### 2024-10-25 scripts/05-exploratory_data_analysis.qmd
simulation revised
simulation revised

```{r}
# Get unique hypothetical
unique_hypothetical <- unique(analysis_data$hypothetical)
print(unique_hypothetical)
```
```{r}
# Calculate the ratio of FALSE to TRUE in the hypothetical column
hypothetical_ratio <- table(simulated_candidate_1$hypothetical)
print(hypothetical_ratio)
false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
print(paste("False to True Ratio:", false_to_true_ratio))
```

@@

```{r}
# Find the maximum difference between start_date and end_date
date_diff <- simulated_candidate_1 %>%
  mutate(date_difference = as.numeric(difftime(end_date, start_date, units = "days"))) %>%
  summarise(max_difference = max(date_difference))

print(date_diff)
```

>>>>

```{r}
# Get unique hypothetical
unique_hypothetical <- unique(analysis_data$hypothetical)
print(unique_hypothetical)
```
```{r}
# Calculate the ratio of FALSE to TRUE in the hypothetical column
hypothetical_ratio <- table(analysis_data$hypothetical)
print(hypothetical_ratio)
false_to_true_ratio <- hypothetical_ratio["FALSE"] / hypothetical_ratio["TRUE"]
print(paste("False to True Ratio:", false_to_true_ratio))
```

@@

```{r}
linear_model <- lm(pct ~ numeric_grade + pollscore + transparency_score + sample_size + partisan + methodology + population + race_id + stage + nationwide_batch + ranked_choice_reallocated + hypothetical, data = analysis_data)
summary(linear_model)
```
